Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-19 paper/paper.tex
new abstract

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe and
  are the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric \lya\ line emission that had evaded theoretical
interpretation so far. 
In this paper we explain these features by two different kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities
(either a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
consistent with a dynamical mass of at 
least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated
baryonic mass.     
We argue that a possible explanation for this excess of
dynamical mass is the presence of a supermassive black hole at the
center of \tol. 
This work suggests the importance of considering multiphase
kinematics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the 
velocities found by our models, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
\end{abstract}

>>>>

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe and
  are the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad symmetric \lya\ line emission that had evaded theoretical
interpretation so far. 
In this paper we explain these features by two different kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities
(either a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
consistent with a dynamical mass of at 
least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated
baryonic mass.     
This work shows the importance of considering multiphase
kinematics and rotation among the possible conditions shaping the
\lya\ spectra of the first galaxies.  
Additionally, if future kinematic maps of \tol\ confirm the 
velocities found by our models, it would provide new
evidence for dwarf galaxies as hosts of supermassive black
holes.  
\end{abstract}
